Metabolic Effects of PCSK9 Inhibition With Evolocumab in Subjects with Elevated Lp(a)

### 2020-01-16 manuscript.Rmd
Results with comments of Erik Stroes

In the present study, we analyzed NMR metabolomics of plasma derived from 30 subjects with elevated Lp(a), using either placebo (n = 14) or PCSK9 inhibitor (evolocumab, n = 16).

@@

The current study included 30 patients (evolocumab, n = 16; placebo, n = 14). 
Baseline characteristics of the two groups were comparable and are provided in Table 1.

@@

However, we identified that the reduction in medium-sized VLDL particles was associated with increasing baseline Lp(a) concentrations (Pearson correlation coefficient -0.5 [-0.8, -0.06]). 
The correlations between baseline Lp(a) concentrations and reduction in other VLDL particles, including extremely large, very large, large, small and very small VLDLs, were -0.1 [-0.6, 0.3], -0.03 [-0.4, 0.4], -0.3 [-0.7, 0.2], -0.1 [-0.7, 0.6], and 0.2 [-0.3, 0.7], respectively.

>>>>

In the present study, we studied 30 subjects with elevated Lp(a), using either placebo (n = 14) or PCSK9 inhibitor (evolocumab, n = 16). 
In particular, we analyzed NMR metabolomics of plasma derived from these participants at baseline and 16 weeks after treatment of evolocumab.

@@

Baseline characteristics of the evolocumab and the placebo group were comparable (Table 1).

@@

Interestingly, we observed that the reduction in medium-sized VLDL particles was associated with increasing baseline Lp(a) concentrations (Pearson correlation coefficient -0.5 [-0.8, -0.06]). 
The correlations between baseline Lp(a) concentrations and reduction in other VLDL particles, including extremely large, very large, large, small and very small VLDLs, were -0.1 [-0.6, 0.3], -0.03 [-0.4, 0.4], -0.3 [-0.7, 0.2], -0.1 [-0.7, 0.6], and 0.2 [-0.3, 0.7], respectively.
